Best Practices for Alchemical Free Energy Calculations [Article v\versionnumber]

### 2024-07-12 paper/manuscript.tex
Add paragraph on newer ABFE restraint schemes
Specifically the quaternion-based restraints of Fu et al. and
the DBC restraint from Salari et al..

@@

The computation of free energies using TI (Sec.n~\ref{subsec:estimators}) is straightforward and the trapezoidal rule is often recommended since it allows unequal spacing of $\vec{\lambda}$ states, which is required to minimize the variance in the free energy estimate, but in principle any good numerical integration method can be used. 
The determination of regions of high curvature when estimating the integral is helpful to determine regions of phase space where more sampling and/or more $\vec{\lambda}$ states are necessary to obtain the best approximation of the integral. Plotting $\vec{\lambda}$ with respect to the gradients at each of the $\vec{\lambda}$ values can be be a helpful diagnostic. 
Additionally, computation of the overall variance of TI requires the calculation of the overall variance of integration, rather than each individual $\Delta$G$_{i,i+1}$ and assuming variances add independently. 
Therefore, $\mathrm{var}$($\Delta$f) = $\sum_{i=1}^{K}w_{k}^2 \mathrm{var}(\frac{du}{d\vec{\lambda}})_{k}$.

>>>>

More recently, restrictive restraint schemes have been proposed that avoid relying on a few critical reference atoms. Instead, these aim to simplify restraint selection by using larger sets of atomic positions in the receptor and ligand. Fu et al. suggested restraining the six relative rigid-body degrees of freedom derived by finding the rotation of the ligand which minimises RMSD to a reference structure of the receptor-ligand complex (after accounting for rotation and translation of the receptor)~\cite{fu2017new}. Salari et al. proposed restraining the ``distance-from-bound-configuration'' (DBC) variable, which is the RMSD of ligand coordinates in the frame of reference of the binding site~\cite{salari2018streamlined, ebrahimi2022symmetry}. This may allow the binding pose to be closely preserved as the ligand intermolecular interactions are removed, but has the disadvantage of coupling the internal and relative external degrees of freedom of the receptor and ligand, preventing easy computation of the standard state correction. This necessitates an additional step where the DBC restraints are released to a single harmonic restraint. Both restraint schemes are implemented in open-source workflows~\cite{fu2021bfee2, fu2022accurate, santiago-mcrae2023computing}.

@@

The computation of free energies using TI (Sec.n~\ref{subsec:estimators}) is straightforward and the trapezoidal rule is often recommended since it allows unequal spacing of $\vec{\lambda}$ states, which is required to minimize the variance in the free energy estimate, but in principle any good numerical integration method can be used. 
The determination of regions of high curvature when estimating the integral is helpful to determine regions of phase space where more sampling and/or more $\vec{\lambda}$ states are necessary to obtain the best approximation of the integral. Plotting $\vec{\lambda}$ with respect to the gradients at each of the $\vec{\lambda}$ values can be a helpful diagnostic. 
Additionally, computation of the overall variance of TI requires the calculation of the overall variance of integration, rather than each individual $\Delta$G$_{i,i+1}$ and assuming variances add independently. 
Therefore, $\mathrm{var}$($\Delta$f) = $\sum_{i=1}^{K}w_{k}^2 \mathrm{var}(\frac{du}{d\vec{\lambda}})_{k}$.
